### 2016-01-18 papers/CAFe/HIPS-paper/multigrid.tex
typo fixing

The multigrid algorithm uses a series of successively coarser grids to interate
approximage solution obtained from the preceeding finer grid.  Higher frequency error modes are
damped out as the solution processes up the grid hierarchy.  At the top of the
hierarchy, an exact solution is obtained and then this solution is iterated and
propogated down the grid hierarchy form coarser to finer grids.  After a few sweeps
up and down the hierarchy the solution with have been obtained on the desired
original grid.

@@

Two levels of the grid hierarchy are shown in \ref{fig_grids} running on a processing computing on
an interior portion of the grid; additional images are computing on regions to the left and right of
the region shown in the figure.  The finist grid (size N) is shown
in the bottom of the figure with cell indices running from (-1:N+1).  Cells 0 and N are shared
between image neighbors to the left and right (indicated by the light blue coloring and the verticle
dashed lines.  These shared cells are computed redundantly on each program image.

The red cells in the figure are computed concurrently on all subimages (one per image).
This distribution of computation over the hierarchical domain of images and subimages
requires communication of boundary regions between the various computational resources.
The communication is shown by arrows in the grid level N of the figure.  Data in cells 1
and 7 must be transferred from the subimage (upwardly pointing arrows) and the shared cell
computations must be copied to the subimage (downwardly pointing arrows) The horizontal
arrows representing data computed and subsequently transferred from the left and right
neighbors.

@@

At the top of the gird hierachy there are sufficiently few cells that an exact solution can be
obtained (perhaps by a non-interpretive method).  This solution is then propogated down the
grid hierarchy as shown in Figure\ref{fig_prolongate}.

@@

The multigrid algorithm has been implemented in Fortran using the CAFe syntax described in
the previous section.  Much of the implementation is straighforward in terms of CAFe are
is only described briefly.

Data coarrays at each grid level are declared, allocated, and initialized on each program image.
These coarrays are then copied to the subimages by the parent, hosting images.  Below we show
the implementation of the relaxation loop on grid level N.  Each iteration step incorporates
concurrent computation on an image and its hosted subimage.  In order to execute concurrently,
we must declare a event variable to allow concurrent execution and then synchronization once
\emph{both} computation ond the subimage \emph{and} the image have completed.

>>>>

The multigrid algorithm uses a series of successively coarser grids to
iteratively approximate the solution obtained from the preceeding
finer grid.  Higher frequency error modes are damped out as the
solution processes up the grid hierarchy.  At the top of the
hierarchy, an exact solution is obtained and then this solution is
iterated and propogated down the grid hierarchy form coarser to finer
grids.  After a few sweeps up and down the hierarchy the solution with
have been obtained on the desired original grid.

@@

Two levels of the grid hierarchy are shown in \ref{fig_grids} running on a processor computing on
an interior portion of the grid; additional images are computing on regions to the left and right of
the region shown in the figure.  The finist grid (size N) is shown
in the bottom of the figure with cell indices running from (-1:N+1).  Cells 0 and N are shared
between image neighbors to the left and right (indicated by the light blue coloring and the vertical
dashed lines).  These shared cells are computed redundantly on each program image.

The red cells in the figure are computed concurrently on all subimages (one per image).
This distribution of computation over the hierarchical domain of images and subimages
requires communication of boundary regions between the various computational resources.
The communication is shown by arrows in the grid level N of the figure.  Data in cells 1
and 7 must be transferred from the subimage (upwardly pointing arrows) and the shared cell
computations must be copied to the subimage (downwardly pointing arrows). The horizontal
arrows represent data computed and subsequently transferred from the left and right
neighbors.

@@

At the top of the grid hierarchy there are sufficiently few cells that an exact solution can be
obtained (perhaps by a non-iterative method).  This solution is then propagated down the
grid hierarchy as shown in Figure\ref{fig_prolongate}.

@@

The multigrid algorithm has been implemented in Fortran using the CAFe
syntax described in the previous section. Data coarrays at each grid
level are declared, allocated, and initialized on each program image.
These coarrays are then copied to the subimages by the parent, hosting
images.  Below we show the implementation of the relaxation loop on
grid level N.  Each iteration step incorporates concurrent computation
on an image and its hosted subimage.  In order to execute
concurrently, we must declare a event variable to allow concurrent
execution and then synchronization once \emph{both} computation ond
the subimage \emph{and} the image have completed.
